Improving content discovery through combining linked data and data mining techniques

### 2016-05-04 report/chapters/01-intro.tex
Halfway through chapter 4
Added more to intro and background

Media companies produce ever larger numbers of articles, videos, podcasts,
games, etc. -- commonly collectively known as ``content''. A successful
content-producing website not only has to develop systems to aid producing and
publishing that content, but there are also demands to engineer effective
mechanisms to aid consumers in finding that content.

@@

\section{Problems}

@@

\item Large organisations can have content across multiple content management
systems, in differing formats and data models. Organisations face a large-scale
enterprise integration problem simply trying to gain a holistic view of all
their content.

@@

@@

\item Research and software tools around the concept of \emph{Linked Data} can
aid us in rapidly acquiring a broad view (perhaps at the expense of depth) of an
organisation's content whilst also providing a platform for simple enrichment of
that content's metadata.

@@

\item We can adapt established machine learning approaches such as clustering
for data published continuously in real time.

\item Many content-producers currently enrich their web pages with small
amounts of semantic metadata to provide better presentation of that content
as it is shared on social media. This enables simple collection of a full
breadth of content with significantly less effort than direct integration
with content management systems.

@@

>>>>

Media companies produce ever larger numbers of articles, videos,
podcasts, games, etc. -- commonly collectively known as ``content'' --
on the World Wide Web. A successful content-producing website not only
has to develop systems to aid producing and publishing that content,
but there are also demands to engineer effective mechanisms to aid
consumers in finding that content.

@@

\section{Problems}
\label{sec:intro-problems}

@@

\item Large organisations can have content across multiple content
  management systems, in differing formats and data models.
  Organisations face large-scale enterprise integration problems
  simply trying to gain a holistic view of all their content.

@@

Many of these problems are felt within the BBC and are potentially
issues in many similar organisations. The BBC website officially
launched in 1997 and many articles from that year are still available
in archived form. Over the last 20 years, multiple content management
systems were created and retired such that today even the active
website is served by a mix of emerging, cutting-edge platforms and
systems that have been running for a number of years.

Technologies such as the World Wide Web and the maturity of the
media industry in its adoption in the last decade creates both an
opportunity to give consumers access to a substantial amount of
media content and a challenge in trying to make cohesive sense of
a diverse range of content, perhaps produced in an organistion that
was traditionally very fragmented as the BBC was.

@@

\item Research and software tools around the concept of
  \emph{Linked Data} can aid us in rapidly acquiring a broad view
  (perhaps initially at the expense of depth) of a organisation's
  content whilst also providing a platform for simple enrichment of
  that content's metadata.

@@

\item Many content-producers currently enrich their web pages with
  small amounts of semantic metadata to provide better presentation of
  that content as it is shared on social media. This enables simple
  collection of a full breadth of content with significantly less
  effort than direct integration with individual content management
  systems.

@@

It is proposed also that all the data acquisition, enrichment and
mappings can be implemented in a general way when semantics and
linked data are used. The standardisations offered by the Semantic
Web and Linked Data research fields provides uniform interfaces and
patterns of data manipulation such that any software produced can be
applied to all of an organisation's content without consideration to
any particular class or type of item. This also does not preclude
including custom business rules later either, where domain experts
can give more guidance to treat data more intelligently.

The core principle in this research is that a generally-applicable
software system provides the best trade-off in terms of processing
the full breadth of content with the least amount of engineering
effort. This can allow media organisations to benefit from things
such as insights from machine learning across their whole corpus with
near-immediate results rather than embarking on large scale enterprise
integration projects over several months or years.

### 2016-05-04 report/chapters/02-background.tex
Halfway through chapter 4
Added more to intro and background

TODO

@@

TODO

>>>>

\emph{Data Mining} is a process for finding knowledge and information
in data sets by drawing on research from artificial intelligence,
machine learning and statistics.\cite{han2011data} In this research,
the focus is on the machine learning aspect with
the data extraction phase implemented using semantics and RDF.

\emph{Machine Learning} broadly breaks down into \emph{supervised}
and \emph{unsupervised} learning. In supervised learning, we have
a task with a clear goal for which we attempt to create a computer
model that can perform that task. In this context, a task might be
to categorise an entity based on its attributed (e.g. diagnose
a particular illness based on symptoms and assessment data from a
patient exam) or perhaps a more numerical goal such as predicting
the chance of rain on a given day based on multiple numerical
readings.

Well-known examples include neural networks, decision trees and or
linear regression. In all supervised learning techniques, we can
normally assess the model's performance against traning data for
which we already know the answers. We can see supervised learning
thus as a computational attempt to extrapolate human knowledge into
a reusable model that can predict or determine things at a speed
and scale humans would not normally be able to work through manually
(e.g. predicting weather with manual calculations or diagnosing
patients more quickly and with greater accuracy).

In unsupervised learning, there is not necessarily a specific goal
against which we can judge the models, but instead we are applying
more exploratory methods to tell us patterns in the data that maybe
we could not see for ourselves (e.g. if we would have to graph trends
over more than two or three dimensions, it is usually difficult to
visualise).

A well-known example is association rule mining that can find
interesting relations in data sets that were perhaps previously
unknwown. A classic implementation of this technique is in
supermarkets and other commercial enterprises where those
organisations seek to find rules and patterns in consumer purchasing
habits so that they can try to promote items that customers might
want to buy based on other items they are currently trying to
purchase.

Another major unsupervised learning technique -- and the focus of
this research -- is \emph{clustering}. In clustering algoriths, we
seek to group similar items or entities together in groups or
\emph{clusters}. Clustering has many applications, but in this
work the focus will be around \emph{hierarchical} clustering which
is effective for grouping together items that appear to be
connected in some way -- in our case that the media content is
connected by virtue of a common theme, topic or genre.

This is based on the premise that users that like a particular
content item might well be interested in other items that mention
the same topics, fall into the same genres or are in some other
way linked.

Note that association rule mining is arguably useful in a similar way.
In the case where we know from user behaviour that users like e.g.
content item $A$ also like content item $B$, then a new user that
likes $A$ but has not read or watched $B$ is likely to be interested
in $B$, so we can suggest it to them.

This is very powerful -- perhaps more powerful as it models how
people behave, not arbitrary tagging or classification of content --
but the focus of this research experiment is to explore the insights
we can get \emph{from the content data alone}. This is appealing
where content producers are struggling to understand their users'
behaviour as collecting meaningful analytics and records of user
behaviour is by no means a trivial endeavour in its own right.

Hierchical clustering differs from, say,
\emph{k-means clustering}\cite{witten2005data} in that
we start with no assumption about the number of clusters or groups
the data will be divided into. This method is generally applied
\emph{agglomeratively} or \emph{divisively}.

In divisive, hierarchical clustering, we start with all elements in
a single cluster and proceed to find divisons that best split that
cluster. This is applied recursively until we generate a
dendrogam\cite{witten2005data} showing a full hierarchy of similarity
between the items or we can halt the division based on some condition,
e.g. only split clusters with a low cohesion below some threshold
and stop on the first attempt to split a cohesive cluster above
that threshold.

Agglomerative, hierarchical clustering goes in the opposite direction
by starting with all items in their own, individual clusters.
The two ``nearest'' clusters are then recursively merged until, again,
we have a full dendrogam or stop before we are about to create a
cluster whose cohesion falls below some threshold.

For media content, agglomerative clustering is a good match for two
practical reasons:

\begin{enumerate}
\item Content is continuously published, so there is potential
  to consider a ``real-time'' clustering system where new items
  arrive in their own cluster initially and are merged into an
  appropriate, established cluster when the next merge is performed.
  This is out of scope for this work, but is an interesting
  consideration if an organisation is to apply this to its real
  content in a way that keeps up to date with new content as it is
  published.
\item The BBC has of the order of tens of millions of pages and thus
  the content is likely to be very diverse with little to no overlap
  between the vast majority of it. The agglomerative model appears to
  fit better with the idea of merging together items where small
  islands of similar content are found and simply ignoring the large
  ``dark matter'' of pages that don't easily merge or for which we
  cannot easily extract good metadata (e.g. if the pages are very
  old).
\end{enumerate}

TODO: linkage and distance

@@

\subsection{Data Fragmentation in Organisations}
\subsection{Enterprise Integration}
\subsection{Organisational Difficulties with Enterprise Integration}
\label{sec:ei-difficulties}
\subsection{Linked Enterprise Data}

### 2016-05-04 report/chapters/03-design.tex
Added more to intro and background

Initially, a business context is described to produce a design for a system
that could be a applied within a media or content-producing organisation. This
context will guide all design decisions.

\section{Context}

TODO

@@

\begin{sidewaysfigure}
  \begin{center}
    \includegraphics[width=\linewidth]{diagrams/usecase.png}
  \end{center}
  \caption{Use case diagram for content clustering system\label{use-case}}
\end{sidewaysfigure}

@@

A \emph{Content Promotion Module} is also depicted as an example application
of the use case where website visitors or audience members then use the
data mining system to find content related to a page they are currently viewing.
The focus of this research is to provide enough visualisation in order to
evaluate the quality of content clusters generated, but it is an important
design principle to consider use cases at all layers of the system.

@@

A core subsystem in the overall system is a conceptual data pipeline whose
input is a URI or IRI identifying a content item published on an organisation's
website and the output is feature sets ready for applying machine learning.

@@

\section{Pipeline Architecture}

TODO

\section{Architecting for Experimentation}

TODO

>>>>

Initially, uses cases and a brief technical architecture for the
proposed system are given and then a theoretical data pipeline is
inductively defined that is the core proposition that extracts
semantics and prepares them for machine learning.

It is assumed that an organisation is already publishing its content
on HTML pages available on the public Internet and that engineers
can make use of existing machine learning algorithms and libraries. It
is out of the scope for the paper to deviate from well-established
machine learning techniques such as hierarchical clustering.

@@

Figure~\ref{fig:use-case} describes how a proposed ``Content Clustering''
software application would be used by established roles in a media
organisation.

\begin{sidewaysfigure}
  \begin{center}
    \includegraphics[width=\linewidth]{diagrams/usecase.png}
  \end{center}
  \caption{Use case diagram for content clustering system\label{fig:use-case}}
\end{sidewaysfigure}

The two main classes of user are those who \emph{produce} content,
e.g. journalists and TV programme makers, and those who will then
benefit from a potential application of these clusters -- in this case,
a feature is proposed that allows website users to find content related
to content they have just finished. These are the people that
\emph{consume} the output of the system.

Note that content production breaks down into several, differing
categories. In figure~\ref{fig:use-case}, we can see two examples of
a journalist writing news articles and a TV production team
publishing information about a particular episode or series. This is
by no means exhaustive as we may well have games developers creating
education games for children, editorial staff publishing recipes that
have appeared on cooking programmes aired by the BBC or pages
delivering the weather forecast for a particular city.

The audience members also break down into multiple categories who
could be reading news articles, watching programmes on on-demand
catch-up TV (e.g. BBC iPlayer) or a child reading educational materials.
These categories are depicted to remind there are multiple ways to
consume content as well as produce it, but it is also important to
note these roles can be transient if we are to promote content truly
on its relevance irrespective of the data store that happens to hold
it.

For example, a child or adult reading informative or educational
material may be interested in a relevant documentary available on
TV catch-up or somebody reading a news article about a topic might
wish to be informed that there are more in-depth educational guides
describing that topic in greater details (e.g. a press release about
a science discovery leading to a full, informative guide on that
field of science).

@@

A \emph{Content Promotion Module} is also depicted as the example application
of the use case where website visitors or audience members then use the
data mining system to find content related to a page they are currently viewing.

The content miner breaks down into two general components: a pipeline
that prepares the data for machine learning and the clustering at the
end on that prepared data. The primary focus of this work is to
evaluate approaches for the former in the form of a
\emph{data pipeline} that uses semantics to take in a content item's
identifer at the source end and produces feature sets for data mining
at the output end. This data pipeline is inductively defined and
designed in the following section.

@@

As stated in the previous sectionh, a core subsystem in the overall
system is a conceptual data pipeline whose input is a URI or IRI
identifying a content item published on an organisation's website and
the output is feature sets ready for applying machine learning.

@@
